# Supplementary Tables and Figures


(ref:german-scale-info-caption) German wording of the HOVS17 items as fielded in the GESIS Panel.

```{r german-scale-info}
 
scale_info |>
  select(Item, `Item Label (GESIS Panel)`, `Wording (German)`) |>
  rename("\\makecell[c]{Item Label\\\\(GESIS Panel)}" = `Item Label (GESIS Panel)` ) |>
  apa_table(longtable = TRUE,
            escape = FALSE,
    font_size = "tiny", 
    caption = "(ref:german-scale-info-caption)",
    align = ifelse(isTRUE(word), c("llcc"),
                   c("m{2.75cm}", "m{1.5cm}", "m{7cm}")),
      stub_indents  = list("Conservation" = c(1:3),
                       "Openness-to-Change" = c(4:8),
                       "Self-Enhancement" = c(9:12),
                       "Self-Transcendence" = c(13:17)),
  )
 
```

\newpage

(ref:scale-descriptives-caption) Descriptive statistics on the scale level.

```{r scale-descriptives}
 
scale_descriptives |> 
    mutate(valid = printnum(valid, digits = 0),
           across(where(is.numeric), ~printnum(.x))) |>
  rename(Dimension = variable,
          "\\emph{n}" = valid,
          "\\emph{M}" = mean,
           "\\emph{SD}" = sd,
          "\\emph{Min}" = min,
          "\\emph{Max}" = max,
         "\\% missing" = missing) |> 

  apa_table(
    stub_indents = list("Raw scores" = c(1:4),
                        "Centered scores" = c(5:8)),
    escape = FALSE,
    longtable = TRUE,
     font_size = "footnotesize", 
     caption = "(ref:scale-descriptives-caption)"
     
  )
 
```

\newpage


(ref:mi-details-caption) Model fits of the configural, metric, and scalar models for each higher-order values and grouping variable.

```{r mi-details}

mi_fit_tab_partial |>  
    filter(Model == "scalar") |>  
    mutate(Model = "partial scalar") |>  
    bind_rows(mi_fit_tab) |>  
    arrange(Dimension, Group, match(Model, c("configural", "metric", "scalar", "partial scalar"))) |>  
    ungroup()|> 
  mutate(Dimension = str_replace_all(Dimension, dimension_renamer),
         Group     = str_replace_all(Group, group_renamer),
         df = printnum(df, digits = 0),
         pvalue = printnum(pvalue, gt1 = FALSE, digits = 3)) |>
  select(-Dimension, -MI_Chen, -MI_BIC) |>
    rename( "$\\chi^2$" = "ChiSq",
           "$\\emph{df}$" = df,
           "$\\emph{p}$" = "pvalue" ) |>
  apa_table(
  stub_indents = list("Conservation" = c(1:12),
                      "Self-Enhancement" = c(13:24),
                      "Openness" = c(25:36),
                      "Self-Transcendence" = c(37:48)
  ),
  escape = FALSE,
  font_size = "footnotesize",
  digits = 2,
  caption = "(ref:mi-details-caption)",
  longtable = TRUE
    )
 
```

\newpage


(ref:item-descriptives-caption) Descriptive statistics on the item level.

```{r item-descriptives}

item_descriptives |> 
  mutate(valid = printnum(valid, digits = 0),
         across(c(mean, sd, missing, kurtosis), ~printnum(.x)),
         across(c(min, max, valid), ~printnum(.x, digits = 0))) |>
  rename(Wording = wording,
         "\\emph{n}" = valid,
         "\\emph{M}" = mean,
         "\\emph{SD}" = sd,
         "\\emph{Min}" = min,
         "\\emph{Max}" = max,
         #"\\% \\ missing" = missing
         ) |> 
  select(-missing, -variable)   |> 
  
  apa_table(longtable = TRUE,
   # stub_indents = list("Raw scores" = c(1:4),
   #                     "Centered" = c(5:8)),
    escape = FALSE,
    #align = "clccccccc",
     align = ifelse(isTRUE(word),
                    "clccccccc", 
                    c("p{0.75cm}", "p{6cm}", rep("p{0.6cm}", 7))),
    font_size = "tiny",
    caption = "(ref:item-descriptives-caption)"
    
  )

```

\newpage


<!-- (ref:r-squared-caption) Variance explained (adjusted $R^2$) in the criteria by the 4 higher-order values or 17 single items. -->

<!-- ```{r r-squared} -->

<!-- adjusted_r_squared |>  -->
<!--   rename(Outcome = "outcome") |> -->
<!--   mutate( -->
<!--     "$\\Delta$" = `Single items` - `Higher-order values`, -->
<!--     across(where(is.numeric), ~papaja::printnum(.x, gt1 = FALSE, digits = 3))) |> -->
<!--   papaja::apa_table(longtable = TRUE, -->
<!--   stub_indents = list("Socio-demographic characteristics" = c(1:4), -->
<!--                       "Personality (Big Five)" = c(5:9), -->
<!--                       "Importance of Life Areas" = c(10:16), -->
<!--                       "Political Orientation" = 17, -->
<!--                       "Well-Being" = c(18:19) -->
<!--   ), -->
<!--   escape = FALSE, -->
<!--   font_size = "footnotesize", -->
<!--   digits = 2, -->
<!--   caption = "(ref:r-squared-caption)", -->
<!--   note = "$\\Delta$ denotes the increment in $R^2$ for the models containing the single-item instead of the 4 higher-order value models as predictors." -->
<!--     ) -->

<!-- ``` -->